An Open Repository of Real-Time COVID-19 Indicators

### 2021-09-10 indicators/paper/responses-to-reviews.tex

\begin{quote}
  Even from a nowcasting perspective, comparisons are all benchmarked against
  cases which are observable in real-time.
\end{quote}

TODO

\begin{quote}
  The strength of observed correlations change (non-monotonically) over time,
  and the implications of this are not discussed.
\end{quote}

While it is difficult to fully explain the changes in correlation---they are
likely due to a variety of changes in reporting practices, health-seeking
behavior, survey response patterns, and so on---one key point is that the
strength of the correlation depends on the overall differences between counties.
That is, if counties have very similar COVID case rates, it is difficult to
achieve a high Spearman correlation between case rates and signals, because
getting the rank correct is difficult. If counties have widely varying COVID
case rates, a signal that provides information about cases will be able to
achieve a higher Spearman correlation.

We have slightly expanded our discussion of Figure 2 to make this point, though
we have tried to keep the discussion brief so as not to sidetrack the main
discussion of the manuscript.

@@

Unfortunately this is not the case: Backlogs and reporting delays are generally
poorly understood and can happen unexpectedly, and users of these datasets often
have to make informed guesses about changes. For instance, many backlogs are due
to retrospective audits of records that uncover cases and deaths that were
incorrectly classified, and can affect case and death estimates months in the
past. Until the audits are complete, policymakers would not know about the
corrections, their magnitude, or the affects they'd have on policy decisions.

Even for predictable backlogs, such as those that occur during major holidays,
the backlog still means policymakers do not have an important signal: If case
and death reporting is suspended for the holiday, knowing that the suspension is
due to the holiday does not help a policymaker judge whether cases are
increasing or decreasing and whether urgent action is required. Outside data
sources would be needed to inform that decision.

TODO Should we add anything to 2.C to make this point more obvious?

\begin{quote}
  As a result, it might be useful to focus quantitative analyses in this paper
  on other attributes of the data or expand analyses to include, e.g.:
  \begin{itemize}
  \item descriptive statistics from each data source, expressed in the units of
    that data source
  \item analysis of how signals differ
  \item analysis of case correlations over time due to discussion of how they
    have evolved over time -- e.g. due to changes in vaccination, testing, etc.
  \item for case studies: I think it would be more powerful to either highlight
    an instance issues were not apparent in the absence of other signals or to
    provide more in depth analysis about a specific policy conclusion that would
    result from use of these signals (or specific examples of
    geographic/temporal variation that the signal data can uniquely inform).
  \end{itemize}
  A compelling framing for the results section might be to include general
  descriptive statistics and then pick case studies that illustrate 2-3 uses of
  the data.
\end{quote}

We appreciate the interest in additional analyses, and our replacement of Figure
6 is partly intended to address this concern about choice of case studies. It
represents an example showing how these data sources can reveal points not
available in other standard data sources, such as case and death data, and serve
to aid public health decision-making.

We have chosen not to include additional descriptive statistics or comparisons
between signals for two reasons. First, given the large number of signals
available in our API, a table of descriptive statistics would be prohibitively
large; this is particularly difficult if one accounts for time and geography by
presenting statistics over time or across space. Second, it's not clear to us
what a reader would gain from such statistics. Because the data is freely
available, a reader interested in any specific signal can quickly investigate it
and explore whatever aspects of it are of interest.

@@

\begin{quote}
  Some of the verb tenses (e.g. line 33) feel awkward: ``The Delphi Group
  **works** (worked) with partner organizations and34 public data sets to build
  a massive database of indicators35 tracking COVID-19 activity and other
  relevant phenomena36 in the United States, which has been publicly available
  and37 continuously updated since April 2020.''
\end{quote}

TODO

\begin{quote}
  It would be helpful to end the introduction with a description of the
  contribution of this paper, rather than other papers.
\end{quote}

We have adjusted the introduction to conclude with the contribution of this
paper, to set it in context against the other papers.

### 2021-09-10 indicators/paper/paper.tex
Another Reviewer 2 comment
Reviewer 2 improvements

In a companion paper, we analyze the utility provided by a core set of the
indicators in COVID-19 forecasting and hotspot prediction models.  In another
companion paper, we elaborate on our research group's (Delphi's) large-scale
public surveys, run in partnership with Facebook and available in aggregate form
in the COVIDcast API.

@@

Figure~\ref{fig:geo_wise_correlation} shows the geo-wise correlations achieved
by the five signals and COVID case rates (from JHU CSSE, smoothed using a 7-day
trailing average), from April 15, 2020 to April 15, 2021. This calculation is
performed over all counties with at least 500 cumulative cases by the end of
this period, and at which all indicators are available (956 counties in
total). The large positive correlations suggest that these signals could be
useful in hotspot detection (identifying counties that have relatively high
COVID activity, at a given time). Somewhat surprisingly, the survey-based
CLI-in-community signal shows the strongest correlations for much of the time
period. This clearly demonstrates the value of a large-scale survey such as CTIS
for tracking symptoms and case trends, especially when other data is unavailable.

>>>>

In a companion paper, we analyze the utility provided by a core set of the
indicators in COVID-19 forecasting and hotspot prediction models.  In another
companion paper, we elaborate on our research group's (Delphi's) large-scale
public surveys, run in partnership with Facebook and available in aggregate form
in the COVIDcast API. This paper focuses on the COVID-19 activity indicators
themselves, describing the data streams, how they are processed and made
publicly available, and insights that can be gained by combining novel data
sources with standard public health surveillance datasets.

@@

Figure~\ref{fig:geo_wise_correlation} shows the geo-wise correlations achieved
by the five signals and COVID case rates (from JHU CSSE, smoothed using a 7-day
trailing average), from April 15, 2020 to April 15, 2021. This calculation is
performed over all counties with at least 500 cumulative cases by the end of
this period, and at which all indicators are available (956 counties in total).
The large positive correlations suggest that these signals could be useful in
hotspot detection (identifying counties that have relatively high COVID
activity, at a given time). Somewhat surprisingly, the survey-based
CLI-in-community signal shows the strongest correlations for much of the time
period. This clearly demonstrates the value of a large-scale survey such as CTIS
for tracking symptoms and case trends, especially when other data is
unavailable. The correlations vary over time in complex ways; while some of this
variation is doubtless due to complex changes in public behavior, reporting and
testing practices, and so on, some is also related to changes in overall
COVID-19 case rates. For example, comparing against
Figure~\ref{fig:time_trends_national}, we observe that correlations drop in
February 2021 for several of the signals, matching when COVID cases also sharply
decline. This decline likely caused the heterogeneity in case rates by county to
decline, making it more difficult for any signal to achieve a high correlation
by county.
